%Input
$\mathbf{x}_{\text{original}}$: Original input text sequence.  
$f(\mathbf{x})$: Target model (e.g., classifier).  
$y_{\text{true}}$: True label of the input sequence.  
$\mathcal{E}(w)$: Counter-fitted word embedding vector for word $w$.  
$\epsilon$: Perturbation limit (maximum number of allowed word replacements).  
$N$: Maximum number of iterations.  

%Output
Adversarial example $\mathbf{x}_{\text{adv}}$ such that:  
\[
f(\mathbf{x}_{\text{adv}}) \neq y_{\text{true}}, \quad \text{with minimal semantic distortion}.
\]

%Formula
1. Initialization:  
   \[
   \mathbf{x}_{\text{adv}}^{(0)} = \mathbf{x}_{\text{original}}.
   \]

2. Word Importance Scoring: For each word $w_i$ in $\mathbf{x}_{\text{adv}}$, compute the impact on the model's prediction:  
     \[
     I(w_i) = |f(\mathbf{x}_{\text{adv}}^{(-i)}) - f(\mathbf{x}_{\text{adv}})|,
     \]  
     where $\mathbf{x}_{\text{adv}}^{(-i)}$ represents $\mathbf{x}_{\text{adv}}$ with $w_i$ masked or removed.

3. Candidate Synonym Generation: Use the counter-fitted word embedding $\mathcal{E}(w_i)$ to find candidate synonyms for $w_i$:  
     \[
     \mathcal{S}_{CF}(w_i) = \{w' \,|\, \text{cosine similarity}(\mathcal{E}(w_i), \mathcal{E}(w')) \geq \tau, w' \neq w_i\},
     \]  
     where $\tau$ is a similarity threshold.

4. Replacement Selection: Replace $w_i$ with the synonym $w_i'$ that maximizes the model loss:  
     \[
     w_i' = \underset{w' \in \mathcal{S}_{CF}(w_i)}{\arg \max} \, \mathcal{L}(f, \mathbf{x}_{\text{adv}}^{(i \rightarrow w')}, y_{\text{true}}),
     \]  
     where $\mathbf{x}_{\text{adv}}^{(i \rightarrow w')}$ is the input with $w_i$ replaced by $w_i'$.

5. Update the Input:  
   \[
   \mathbf{x}_{\text{adv}}^{(t+1)} = \mathbf{x}_{\text{adv}}^{(t)} \, \text{with the replaced word}.
   \]

6. Stopping Condition: If $f(\mathbf{x}_{\text{adv}}^{(t+1)}) \neq y_{\text{true}}$, or if the number of replaced words exceeds $\epsilon$, terminate the attack.

%Explanation
The Counter-Fitted Word Embedding Swap attack generates adversarial examples for text classifiers by substituting words with semantically similar alternatives identified using counter-fitted word embeddings.

1.Objective: The attack aims to mislead the model by subtly replacing words while preserving the original semantic meaning.  

2.Word Importance Scoring: Words that contribute the most to the model's prediction are identified through heuristic importance scores.  

3.Synonym Selection: Counter-fitted word embeddings are used to ensure replacements are semantically similar. These embeddings are specifically designed to reduce distances between synonyms and increase distances between antonyms, ensuring meaningful perturbations.  

4.Iterative Refinement: Words are replaced iteratively based on their importance and the effect of their replacement on the model's output.  

5.Semantic Preservation: By using counter-fitted embeddings and cosine similarity, the attack maintains the semantic integrity of the original text, ensuring human readability of the adversarial examples.  

6.Advantages: This method is a black-box attack as it does not require access to the model’s gradients, making it effective for scenarios where the model's internal workings are unknown.
