%Input
$x$: The input image. 
$f$: The binary classifier function. 
$\hat{r}$: The resulting perturbation. 
$x_0$: The initial image (set to $x$).
$i$: The iteration counter. 
$\text{sign}(f(x))$: The sign of the classifier's output, indicating the class. 
$r_i$: The perturbation at iteration $i$. 
$\nabla f(x)$: The gradient of the classifier function at $x$.
$\hat{k}(x)$: The predicted class label of image $x$. 
$k$: A class different from the initial predicted class $\hat{k}(x_0)$. 
$w'_k$: The difference in the gradients of the $k$-th and the initial class functions. 
$f'_k$: The difference in the outputs of the $k$-th and the initial class functions. 
$\hat{l}$: The class with the minimum ratio of $|f'_k|$ to $\|w'_k\|_2$.
$\nabla f_k(x)$: The gradient of the $k$-th class function at $x$.

%Output
The DeepFool for binary classifier algorithm for binary classifiers generates a perturbation $\hat{r}$ to misclassify an image $x$. The algorithm works by iteratively updating the perturbation until the classifier's prediction changes. It begins with initializing the perturbation and iteration counter. During each iteration, the perturbation $r_i$ is computed based on the gradient of the classifier function and is applied to the image. The process continues until the image's classification changes. The final perturbation $\hat{r}$ is the sum of all individual perturbations computed during the iterations. This perturbation is designed to minimally alter the image while causing a misclassification.

%Formula
 The DeepFool algorithm for generating adversarial perturbations for binary classifiers can be formulated as follows:

\begin{enumerate}
    \item \textbf{Input Parameters:}  
    \begin{align*}
    x &: \text{Input image}, \\
    f &: \text{Classifier function}.
    \end{align*}

    \item \textbf{Initialization:}  
    Set the initial perturbed image and iteration counter:
    \[
    x_0 = x, \quad i = 0.
    \]

    \item \textbf{Iterative Update:}  
    While the classifier prediction remains unchanged:
    \[
    \text{sign}(f(x_i)) = \text{sign}(f(x_0)),
    \]
    perform the following steps:
    \begin{enumerate}
        \item Compute the perturbation at iteration $i$:
        \[
        r_i = -\frac{f(x_i)}{\|\nabla f(x_i)\|_2^2} \nabla f(x_i).
        \]
        \item Update the perturbed image:
        \[
        x_{i+1} = x_i + r_i.
        \]
        \item Increment the iteration counter:
        \[
        i \gets i + 1.
        \]
    \end{enumerate}

    \item \textbf{Output:}  
    Return the cumulative perturbation:
    \[
    \hat{r} = \sum_i r_i.
    \]
\end{enumerate}


%Explanation
\textbf{Initialization:} 
Set the initial perturbed image $x_0$ to the input image $x$. 
Initialize the iteration counter $i$ to 0.
\textbf{Iteration Loop:} 
Continue iterating while the classifier's sign for $x_i$ is the same as for $x_0$.
\textbf{Perturbation Calculation:}
Calculate the perturbation $r_i$ as the negative of the classifier's output scaled by the gradient's norm squared. 
Update the perturbed image $x_{i+1}$ by adding $r_i$ to $x_i$.
\textbf{Update:} 
Increment the iteration counter $i$ by 1.
\textbf{Return:}
Return the accumulated perturbation $\hat{r}$ as the sum of all $r_i$.





