%Input
$\mathbf{x}_{\text{original}}$: Original input text sequence.  
$f(\mathbf{x})$: Target model (e.g., classifier).  
$y_{\text{true}}$: True label of the input sequence.  
$\mathcal{S}_{WN}(w)$: Set of synonyms for word $w$ obtained from WordNet.  
$\epsilon$: Perturbation limit (maximum allowed word replacements).  
$N$: Maximum number of iterations.

%Output
Adversarial example $\mathbf{x}_{\text{adv}}$ such that:  
\[
f(\mathbf{x}_{\text{adv}}) \neq y_{\text{true}}, \quad \text{with minimal semantic distortion}.
\]

%Formula
1. Initialization:  
   \[
   \mathbf{x}_{\text{adv}}^{(0)} = \mathbf{x}_{\text{original}}.
   \]

2. Word Importance Scoring:  
   - For each word $w_i$ in $\mathbf{x}_{\text{adv}}$, compute the impact on the model's prediction:  
     \[
     I(w_i) = |f(\mathbf{x}_{\text{adv}}^{(-i)}) - f(\mathbf{x}_{\text{adv}})|,
     \]  
     where $\mathbf{x}_{\text{adv}}^{(-i)}$ represents $\mathbf{x}_{\text{adv}}$ with $w_i$ removed or masked.

3. Synonym Replacement:  
   - For the most important word $w_i$ (highest $I(w_i)$):  
     \[
     w_i' = \underset{w' \in \mathcal{S}_{WN}(w_i)}{\arg \min} \, d(w_i, w'),
     \]  
     where $d(w_i, w')$ is a semantic similarity metric ensuring minimal distortion.

4. Update the Input:  
   \[
   \mathbf{x}_{\text{adv}}^{(t+1)} = \mathbf{x}_{\text{adv}}^{(t)} \, \text{with } w_i \text{ replaced by } w_i'.
   \]

5. Stopping Condition:  
   - If $f(\mathbf{x}_{\text{adv}}^{(t+1)}) \neq y_{\text{true}}$, or if the number of replacements exceeds $\epsilon$, terminate the attack.

%Explanation
The WordNet-based synonym swap attack is a heuristic approach designed for adversarial attacks on text classifiers.

1. Objective: To subtly alter the text input by replacing words with their synonyms, causing the model to misclassify while preserving the original semantic meaning.  

2. Word Importance Scoring: Identifies the most influential words for the model's prediction by analyzing their impact on the prediction score.  

3. Synonym Selection: Uses WordNet to find semantically similar synonyms. A similarity metric ensures minimal semantic distortion, maintaining the human readability of the adversarial text.  

4. Iterative Refinement: Iteratively modifies the input by replacing important words with their synonyms until the attack succeeds or the perturbation budget ($\epsilon$) is exhausted.  

5. Advantage: This attack is non-gradient-based and operates in a black-box setting, making it suitable for scenarios where the target model's gradients or parameters are inaccessible.
