%Input
$\hat{A}$: The variable being optimized over, representing a matrix or parameter to be estimated.
$L_t(\hat{A})$: The objective function that depends on $\hat{A}$, which is to be maximized.
$\mathbf{A}$: The original matrix or parameter.
$\hat{\mathbf{A}}$: The estimated matrix or parameter.
$\rho$: A given threshold value that constrains the sum of absolute differences.
$\sum_{i<j}$: Summation operator over all pairs $(i, j)$ where $i < j$.
$|\mathbf{A}_{ij} - \hat{\mathbf{A}}_{ij}|$: The absolute difference between the elements of matrices $\mathbf{A}$ and $\hat{\mathbf{A}}$ at position $(i, j)$.

%Output:
$\hat{A}^*$: The optimal solution for the matrix or parameter that maximizes the objective function $L_t(\hat{A})$ while satisfying the constraint.

$L_t(\hat{A}^*)$: The maximum value of the objective function $L_t(\hat{A})$ achieved with the optimal $\hat{A}^*$.

$\sum_{i<j} |\mathbf{A}_{ij} - \hat{\mathbf{A}}_{ij}|$: The sum of the absolute differences between the elements of the original matrix $\mathbf{A}$ and the estimated matrix $\hat{\mathbf{A}}$ at position $(i, j)$, constrained to be less than or equal to $\rho$.

%Formula
The optimization problem can be expressed as:
$\arg \max_{\hat{A}} L_t(\hat{A}) \quad \text{subject to} \quad \sum_{i<j} |\mathbf{A}_{ij} - \hat{\mathbf{A}}_{ij}| \leq \rho$

%Explanation
$ \arg \max_{\hat{A}} L_t(\hat{A})$
\textbf{arg max}: This operator finds the argument \( \hat{A} \) that maximizes the function $ L_t(\hat{A})$
$\hat{A}$ The variable being optimized over.
$L_t(\hat{A})$ The objective function to be maximized, which depends on $\hat{A}$
\textbf{subject to}:
Indicates that the optimization is performed under certain constraints.
$ \sum_{i<j} |\mathbf{A}_{ij} - \hat{\mathbf{A}}_{ij}| \leq \rho $
$ \sum_{i<j}$ Summation over all pairs $ (i, j) $ where $ i < j $
$ |\mathbf{A}_{ij} - \hat{\mathbf{A}}_{ij}| $ 
The absolute difference between the elements of the matrices $ \mathbf{A} $ 
and $ \hat{\mathbf{A}} $ at position $ (i, j)$
$ \leq \rho $ 
The sum of the absolute differences is constrained to be less than or equal to $ \rho$, where $\rho $ is a given threshold.
Indirect Attack: The attack is located on a link that is not connected to the target node to make the attack more covert.